### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Side-channel Leakages}
\subsection{Secret-dependent Control Flow Transfers}

>>>>

\section{Side-channel Leakages}
\subsection{Secret-dependent Control Flow Transfers}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
void example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    printf("branch 1\n");
  } else {
    printf("branch 2\n");
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_key]    
and   eax, [addr_message] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}

\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example6(uint16_t k) {
  int res;
  if (k > 8) {
    res = 0;
  } else {
    res = 1;
  }
  return res;
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
xor   eax, eax
cmp   [addr_k], 8
setbe  al
xor    edx, edx
ret
\end{lstlisting}
\end{minipage}
\caption{A Serious Leakage}\label{fig:chapter3:cf}
\end{figure}
